\bibitem{mell2011nist}Mell, P., Grance, T. \& Others The NIST definition of cloud computing. (Computer Security Division, Information Technology Laboratory, National …,2011)

\bibitem{atlam2017integration}Atlam, H., Alenezi, A., Alharthi, A., Walters, R. \& Wills, G. Integration of cloud computing with internet of things: challenges and open issues. {\em 2017 IEEE International Conference On Internet Of Things (iThings) And IEEE Green Computing And Communications (GreenCom) And IEEE Cyber, Physical And Social Computing (CPSCom) And IEEE Smart Data (SmartData)}. pp. 670-675 (2017)

\bibitem{khan2019edge}Khan, W., Ahmed, E., Hakak, S., Yaqoob, I. \& Ahmed, A. Edge computing: A survey. {\em Future Generation Computer Systems}. \textbf{97} pp. 219-235 (2019)

\bibitem{gokhale2018introduction}Gokhale, P., Bhat, O. \& Bhat, S. Introduction to IOT. {\em International Advanced Research Journal In Science, Engineering And Technology}. \textbf{5}, 41-44 (2018)

\bibitem{iorga2018fog}Iorga, M., Feldman, L., Barton, R., Martin, M., Goren, N., Mahmoudi, C. \& Others Fog computing conceptual model.  (2018)

\bibitem{sahni2018data}Sahni, Y., Cao, J. \& Yang, L. Data-aware task allocation for achieving low latency in collaborative edge computing. {\em IEEE Internet Of Things Journal}. \textbf{6}, 3512-3524 (2018)

\bibitem{yi2015fog}Yi, S., Hao, Z., Qin, Z. \& Li, Q. Fog computing: Platform and applications. {\em 2015 Third IEEE Workshop On Hot Topics In Web Systems And Technologies (HotWeb)}. pp. 73-78 (2015)

\bibitem{atlam2018fog}Atlam, H., Walters, R. \& Wills, G. Fog computing and the internet of things: A review. {\em Big Data And Cognitive Computing}. \textbf{2}, 10 (2018)

\bibitem{heck2010software}Heck, P., Klabbers, M. \& Eekelen, M. A software product certification model. {\em Software Quality Journal}. \textbf{18}, 37-55 (2010)

\bibitem{anisetti2017semi}Anisetti, M., Ardagna, C., Damiani, E. \& Gaudenzi, F. A semi-automatic and trustworthy scheme for continuous cloud service certification. {\em IEEE Transactions On Services Computing}. \textbf{13}, 30-43 (2017)

\bibitem{aslam2020fonac}Aslam, M., Mohsin, B., Nasir, A. \& Raza, S. FoNAC-an automated fog node audit and certification scheme. {\em Computers \& Security}. \textbf{93} pp. 101759 (2020)


\bibitem{baldini2016security}Baldini, G., Skarmeta, A., Fourneret, E., Neisse, R., Legeard, B. \& Le Gall, F. Security certification and labelling in Internet of Things. {\em 2016 IEEE 3rd World Forum On Internet Of Things (WF-IoT)}. pp. 627-632 (2016)

\bibitem{ardagna2015security}Ardagna, C., Asal, R., Damiani, E. \& Vu, Q. From security to assurance in the cloud: A survey. {\em ACM Computing Surveys (CSUR)}. \textbf{48}, 1-50 (2015)

\bibitem{infrastructure2002common}Infrastructure, P. \& Profile, T. Common criteria for information technology security evaluation. {\em National Security Agency}. (2002)

\bibitem{anisetti2013test}Anisetti, M., Ardagna, C., Damiani, E. \& Saonara, F. A test-based security certification scheme for web services. {\em ACM Transactions On The Web (TWEB)}. \textbf{7}, 1-41 (2013)

\bibitem{CSATrustSTAR}Cloud Security Alliance, Security CSATrust \& Assurance Registry (STAR). (\url{https://cloudsecurityalliance.org/star/}), Accessed: 2022-08-29

\bibitem{IBMConfChange}Configuration Change Overview. (\url{https://www.ibm.com/docs/en/mfnp/7.6.0?topic=changes-configuration-change-overview}), Accessed: 2022-08-29

\bibitem{mateusz2022flex}Mateusz Ciok, K., Pascual Espada, J. \& González Crespo, R. Flex-request: Library to make remote changes in the communication of IoT devices. {\em Expert Systems}. pp. e12994 (2022)

\bibitem{kaluvuri2014quantitative}Kaluvuri, S., Bezzi, M. \& Roudier, Y. A quantitative analysis of common criteria certification practice. {\em International Conference On Trust, Privacy And Security In Digital Business}. pp. 132-143 (2014)

\bibitem{keblawi2006applying}Keblawi, F. \& Sullivan, D. Applying the common criteria in systems engineering. {\em IEEE Security \& Privacy}. \textbf{4}, 50-55 (2006)

\bibitem{ICSAFw}Labs, I. ICSA Labs IoT Security Testing Framework. (\url{https://www.icsalabs.com/technology-program/iot-testing}), Accessed: 2022-08-29

\bibitem{surveyIOT}Matheu, S., Hernández-Ramos, J., Skarmeta, A. \& Baldini, G. A Survey of Cybersecurity Certification for the Internet of Things. {\em ACM Comput. Surv.}. \textbf{53} (2020,12), https://doi.org/10.1145/3410160

\bibitem{orangeBook}Latham, D. Department of defense trusted computer system evaluation criteria. {\em Department Of Defense}. \textbf{198} (1986)

\bibitem{ITSEC}Jahl, C. The information technology security evaluation criteria. {\em Proceedings-13th International Conference On Software Engineering}. pp. 306-307 (1991)

\bibitem{orangeBookDeath}Lipner, S. The birth and death of the orange book. {\em IEEE Annals Of The History Of Computing}. \textbf{37}, 19-31 (2015)

\bibitem{CTCPEC}Bacic, E. The Canadian trusted computer product evaluation criteria. {\em [1990] Proceedings Of The Sixth Annual Computer Security Applications Conference}. pp. 188-196 (1990)

\bibitem{CCProducts}Common Criteria Certified Products. (https://www.commoncriteriaportal.org/products/), Accessed: 2022-08-29

\bibitem{ardagna2014management}Ardagna, C., Asal, R., Damiani, E. \& Vu, Q. On the management of cloud non-functional properties: The cloud transparency toolkit. {\em 2014 6th International Conference On New Technologies, Mobility And Security (NTMS)}. pp. 1-4 (2014)

\bibitem{goertzel2007software}Goertzel, K., Winograd, T., McKinley, H., Oh, L., Colon, M., McGibbon, T., Fedchak, E. \& Vienneau, R. Software security assurance: a state-of-art report (sar). (INFORMATION ASSURANCE TECHNOLOGY ANALYSIS CENTER (IATAC) HERNDON VA,2007)

\bibitem{article}Ardagna, C., Asal, R., Damiani, E. \& Vu, Q. From Security to Assurance in the Cloud. {\em ACM Computing Surveys}. \textbf{48} pp. 1-50 (2015,7)

\bibitem{mahmud2018fog}Mahmud, R., Kotagiri, R. \& Buyya, R. Fog computing: A taxonomy, survey and future directions. {\em Internet Of Everything}. pp. 103-130 (2018)

\bibitem{macneil2006comply}MacNeil, I. \& Li, X. “Comply or Explain”: market discipline and non-compliance with the Combined Code. {\em Corporate Governance: An International Review}. \textbf{14}, 486-496 (2006)

\bibitem{anisetti2022multi}Anisetti, M., Ardagna, C. \& Bena, N. Multi-Dimensional Certification of Modern Distributed Systems. {\em IEEE Transactions On Services Computing}. (2022)

\bibitem{chen2013verification}Chen, M., Tan, T., Sun, J., Liu, Y., Pang, J. \& Li, X. Verification of functional and non-functional requirements of web service composition. {\em International Conference On Formal Engineering Methods}. pp. 313-328 (2013)

\bibitem{pub2005minimum}Pub, F. Minimum security requirements for federal information and information systems.  (2005)

\bibitem{nasiri2019security}Nasiri, S., Sadoughi, F., Tadayon, M. \& Dehnad, A. Security requirements of internet of things-based healthcare system: a survey study. {\em Acta Informatica Medica}. \textbf{27}, 253 (2019)

\bibitem{daemen1999aes}Daemen, J. \& Rijmen, V. AES proposal: Rijndael. (Gaithersburg, MD, USA,1999)

\bibitem{fischer2017dod}Fischer, T. DoD 5220.22-m data wipe method [US DOD wipe standard]. (Retrieved from Lifewire: https://www. lifewire. com/dod-5220-22-m-2625856,2017)

\bibitem{OpenSSLMan}Young, E. \& Hudson, T. OpenSSL Manual. , (\url{https://www.openssl.org/docs/man3.0/man7/crypto.html}), Accessed: 2022-09-13
